---
title: "examples"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First load the package:

```{r setup}
library(ghgportalR)
library(httr2) # should be loaded automatically, here just in case...
```

Then we have to get the token from your username and password. In the following example username and passwords are from system variables, in order not to make them visible, but you can substitute `api_username` and `api_password` with yours.

```{r, results=FALSE}
api_username <- Sys.getenv("ghgportal_API_USERNAME")
api_password <- Sys.getenv("ghgportal_API_PASSWORD")
                           
reply <- get_token(uname = api_username, upass = api_password)
```

We then select just the token bit from the output:
```{r}
my_token <- reply$token
```

Now with the token we can start querying the database, starting from a list of projects assigned to the user:
```{r}
get_projects(my_token)
```
