---
title: "Vignette examples -  ghgportalR package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

After you have installed the package with devtools (instructions are in the readme file of the repository), load the package:

```{r setup}
# Suppress the vignette title check warning
options(rmarkdown.html_vignette.check_title = FALSE)
library(ghgportalR)
library(httr2) # should be loaded automatically, here just in case...
```

Then we have to get the token from your username and password. In the following example username and passwords are from system variables, in order not to make them visible, but you can substitute `api_username` and `api_password` with yours.

```{r, results=FALSE}
api_username <- Sys.getenv("ghgportal_API_USERNAME")
api_password <- Sys.getenv("ghgportal_API_PASSWORD")
                           
reply <- get_token(uname = api_username, upass = api_password)
```



We then select just the token bit from the output:
```{r}
my_token <- reply$token
```

Now with the token we can start querying the database, starting from a list of projects assigned to the user:
```{r}
get_projects(my_token)
```


We can now query a specific project. In this case we want to select project 1: 

```{r}
all_meas <- get_meas(my_token, project_id = 1)
```

Just in case, the parameter `project_id` refers to the number in the column `"project"` and not `"id"`.  


There might be errors in some series (mainly due to the uploader not having yet accepted or validated), and you might not be able to retrieve some of them. To check which ones we can retrieve, we can use the following function:

```{r}
all_series <- get_all_series(token = my_token, meas_id = meas)
available_series <- all_series$all_series[which(all_series$data_check == "available")]
length(available_series)
```
Some are not available:

```{r}
all_series$data_check
```
And we can see that in many cases the uploaders are not yet ready with the measurements.

Now we can query one single measurement series from the available ones:
```{r}
available_id <- all_meas$id[which(all_series$data_check == "available")]
series <- get_series(token = my_token, meas_id = available_id[1])
```

Here is where things get complicated, since the database structure is a nested array. Each series consists of a vector of values (the measurement) of an arbitrary length, plus some associated metadata. The object returned (a JSON object) is read as a list of lists.  
  
One of the metadata is the `siteid` field in each second order list.  
We can get a matrix with all the `siteid` in a measurement series
```{r}
subsite_info <- subsiteID_names(series)
subsite_info
```

Same can be done with the sampling points:
```{r}
points_info <- point_names(series)
points_info
```

Now, one thing we migth want to do is, for example, select only the measurements with a certain subsite ID. We created a specific function for that:

```{r}
filtered_series_bysubsiteID <- subsiteID_filter(series, subsiteID_value="DP-MC")
```

Another possibility is to inspect one single element of a series, obtaining a more readable output with the function `process_single_series`, for example here if we want to visualize the element 11:
```{r}
process_single_series(series, 11)
```
